Introduction

### 2015-07-21 dissertation/problems.tex
Some text around stability

\begin{problem}
The complexity of SPARQL is high.
\end{problem}

>>>>

It was found in \cite{perez2009semantics} that

\begin{problem}
SPARQL has some highly complex parts.
\end{problem}

In particular, nested \sparql{OPTIONAL}s will be difficult to
evaluate. A Cartesian join is also likely to cause trouble, but even
seemingly straightforward queries may be heavy. We also note from
experience that:

\begin{problem}
Public endpoints may have unpredictable usage patterns.
\end{problem}

Caching plays an important role in the Web architecture
\cite{webarch}, because previous responses may be reused to satisfy a
current request. However, there are many problems that need to be
solved to use it for SPARQL query evaluation:

\begin{problem}
SPARQL endpoints, which are based on HTTP, will only enable caching
syntactically identical queries by  default.
\end{problem}

\begin{problem}
Determining that two queries will return the exact same answer is a
complex problem.
\end{problem}

\begin{problem}
It is not known how much of the Semantic Web exposes information that
could be used in HTTP caching.
\end{problem}
